# Evidence synthesis: Situating iyarn + directions for evaluation and development {#evidence-synthesis}

We have developed a synthesis of evidence, based on the program logic matrix \@ref(model) and questions. These syntheses should:

* Represent the evidence base x draws on and give language to that
* Be shareable providing stakeholders with an understanding of the research background
* Support development of x by pointing to gaps (in the tool, or existing evidence) and methods for evaluation

In each of the syntheses, the sections and purposes should:

* Provide a key summary
* Highlight implications  
* Point to lessons for future work
* Link to practical use cases (including those expressed in the developed scenarios). 

These resources comprise:

1. <span style="color:#0d41d1">Three evidence syntheses </span>.
1. <span style="color:#32cd32">Three Frequently Asked Questions (FAQ) summaries, with questions and answers directly linked back to the longer and fully referenced evidence syntheses</span>.


## First question space {#synthesis-checkins}

```{r synthesis-checkin, fig.cap="evidence synthesis: What is the evidence for...", echo=F}

include_doc(my_file = "data/04-synthesis/04-synthesis-checkins.docx")

```

### Checkins FAQ

```{r synthesis-checkin-faq, fig.cap="evidence synthesis for...", echo=F}

include_doc(my_file = "data/04-synthesis/04-synthesis-checkins-FAQ.docx")

```
