# An evidence informed tool: Identifying factors {#factors}

## Background 

This section addresses the following questions in the model, through evidence synthesis, resource creation and mapping, and resources for stakeholders. Specifically, we analyse, evaluation of existing models of x and behavioural change, existing resources, and design research regarding ... 

1.	.
2.	.
3.	.

## Factors in the space

### Background

Work was undertaken to align with evidence-based models of x, to identify the key _factors_ that constitute x, and their relationship to y.


### Document 1

Based on this initial mapping.. 

A document setting out models in the space. 


## intervention designs {#intervention-design}

Document setting out models for intervention in the space. 

### Resource mapping

Documents mapping a range of existing external resources to the model in \@ref(fig:mapping).

```{r mapping, fig.cap="Mapping available resources to intervention model", echo=F}

pacman::p_load(htmltools)
pacman::p_load(reactable)
pacman::p_load(magrittr)

# resource_map <- "data/05-intervention-files/05-04-resource-mapping.xlsx"
# #openxlsx::getSheetNames(resource_map)
# 
# map <- lapply(seq(2,7), function(x){
#   y <- openxlsx::read.xlsx(resource_map, fillMergedCells = TRUE, sheet=x, startRow=2, skipEmptyCols = T)
#   y$segment <- openxlsx::getSheetNames(resource_map)[x]
#   y
# })
# 
# #map <- do.call("rbind", map)
# map <- plyr::rbind.fill(map)

map <- force(mtcars)

map_colour <- tibble::tibble(
  carb = unique(map$carb),
  shade = c("185,220,255","255,189,222","255,191,159","72,254,167","211,181,233","255,227,139") #blue, pink, orange, mint, purple, yellow
)

map <- dplyr::left_join(map,map_colour,by=c("carb"))
  
#sapply(strsplit(map$shade, ","), rgb_2_hex)
map$shade <- rgb(read.table(text=map$shade,sep=',',strip.white = TRUE,col.names=c("r","g","b")),maxColorValue=255)

#map <- map %>% dplyr::relocate(Description, .after = segment) %>% dplyr::relocate(segment, .before = "Sub-Segment")


if (knitr::is_html_output()) {

  pacman::p_load(tippy)
  render_tippy <- function(text, tooltip){
  div(style = "text-decoration: underline;
                text-decoration-style: dotted;
                text-decoration-color: #FF6B00;
                cursor: info;
                white-space: nowrap;
                overflow: hidden;
                text-overflow: ellipsis;",
    tippy(text = text, tooltip = tooltip)
  )
  }

show_map <- reactable(map, 
                      wrap = FALSE,
            style = list(fontFamily = "Work Sans, sans-serif", fontSize = "10px"),
            compact = TRUE,
            filterable = TRUE,
            minRows = 10,
            searchable = TRUE,
            defaultSorted = c("carb"),
            highlight = TRUE,
            bordered = TRUE,
            resizable = TRUE,
            defaultColDef = colDef(
              header = function(value)
                gsub(".", " ", value, fixed = TRUE),
              headerStyle = list(background = "#f7f7f8")
            ),
            columns = list(
              shade = colDef(show = F),
              URL = colDef(style = list(fontsize = "0.5rem")),
              Description = colDef(
                html = TRUE,
                cell = function(value, index, name) {
                  render_tippy(text = value, tooltip = value)
                }
              )
            ),
            rowStyle = function(index) {
              list(background = map[index,"shade"])
            }
)
show_map
} else {
  
   # 
   # show_map_all <- reactable(
   #   map,
   #   wrap = FALSE,
   #   style = list(fontFamily = "Work Sans, sans-serif", fontSize = "10px"),
   #   minRows = 10,
   #   defaultSorted = c("segment"),
   #   bordered = TRUE,
   #   defaultColDef = colDef(
   #     header = function(value)
   #       gsub(".", " ", value, fixed = TRUE),
   #     headerStyle = list(background = "#f7f7f8")
   #   ),
   #   columns = list(shade = colDef(show = F)),
   #   rowStyle = function(index) {
   #     list(background = map[index, "shade"])
   #   }
   #   #pagination = FALSE
   # )
   # pacman::p_load(htmlwidgets)
   # pacman::p_load(webshot2)
   # html <- "data/05-intervention-files/rtable.html"
   # saveWidget(show_map_all, html)
   # 
   # webshot2::webshot(html, "data/05-intervention-files/wellbeing_mapping2.pdf")
   # 
   # # you can also export to pdf
   # 
    chunk_lab <- knitr::opts_current$get()$label

    knitr::raw_latex(paste0("\n\n\\includepdf[pages=-,noautoscale, width=205mm, height = 240mm, pagecommand={}]{data/05-intervention-files/mapping2.pdf}\\label{fig:",chunk_lab,"}\n\n"))
  }
   
```


```{r factors-pdf-demo, fig.cap="and just to show the pdf version...", echo=F}

include_doc(my_file = "data/05-intervention-files/mapping2.pdf")

```


**Inclusion criteria:**

* here
* and here

## Stakeholder resources

Based on the research, two key stakeholder-oriented resources were created:

1. A powerpoint resource, intended to introduce factors ...
1. A guide which provides an overview of the background to x and its use in classes...

These can be augmented with the resource mapping... 
