--- 
title: "projectname: Developing the Evidence Base: Final Project Report \\ \\"
subtitle: "Knight, S., (2022). projectname: Developing the Evidence Base – Final Project Report. University of Technology Sydney."
author: "Simon Knight"
date: "`r Sys.Date()`"
github-repo: sjgknight/md-generic
site: "bookdown::bookdown_site"
url: https\://sjgknight.com
book_filename: "UTS-final-report"
biblio-style: apalike
split_bib: no
nocite: '@*'
bibliography: [book.bib, packages.bib]
link-citations: yes
description: "Knight, S., (2022). projectname: Developing the Evidence Base – Final Project Report. University of Technology Sydney."
sharing: no
params:
  bibupdate:
    label: "Update bibliography (true to update, false to skip)"
    value: FALSE
    input: radio
    choices: [TRUE,FALSE]
output:
  bookdown::pdf_book:
    includes:
      in_header: preamble.tex
      before_body: before_body.tex
    book_filename: "UTS-final-report"
    fig_caption: yes
    css: "style.css"
    output_dir: "_book/pdf/"
    keep_tex: true
    latex_engine: xelatex
    titlepage: true
    titlepage-color: 0d41d1
    titlepage-text-color: f5f4f5
    titlepage-rule-color: f5f4f5
    titlepage-rule-height: 1
    language:
      ui:
        chapter_name: "Part "
  bookdown::bs4_book:
    repo: https://github.com/sjgknight/md-generic
    sharing: no
    download: ["pdf", "epub"]
    output_dir: "_book/bs4_book"
    css: "style.css"
header-includes:
  - \usepackage{xcolor}
  - \usepackage{titling}
  - \usepackage{pdfpages}
  - \usepackage{fancyhdr}
  - \usepackage{floatrow}
  - \usepackage{caption}
  - \definecolor{bluerich}{RGB}{13,65,209}
  - \usepackage{titling}
  - \pretitle{\begin{center}
  - \floatsetup[figure]{capposition=top}
  - \includegraphics[width=2in,height=2in]{data/00-misc/logo.png}\LARGE\\}
  - \posttitle{\end{center}}
  - \setlength{\headheight}{23pt}
  - \addtolength{\topmargin}{-11pt}
  - \fancyfoot[L]{\footnotesize\textcolor{bluerich}{\textbf{University of Technology Sydney} \\ Centre for Research on Education in a Digital Society (CREDS) \\ TD School}}
  - \fancyfoot[C]{\thepage}
  - \renewcommand{\footrulewidth}{2pt}
  - \fancyhead[L]{\itshape\nouppercase{\rightmark}}
  - \fancyhead[R]{Section \arabic{chapter}}
  - \pagestyle{fancy}
documentclass: book
---

# Working with this document

This report was written as a wrapper site to compile a set of outputs, along with their rationale and the overarching narrative. It was written using a tool called *bookdown*, with the aim to make it easier to navigate the materials without getting lost (and to support export to other formats like PDF). 

This dummy demonstates two key things:

1. The - very messy - rureporting package, primarily the function `include_doc` which will either iframe embed documents (pptx, docx, pdf - all converted to pdf); or merge docs into a single PDF; a function `include_frag` will take a docx and convert to markdown for inclusion in the html. 
2. Show how the files were setup...it's quite messy, but without playing more with `LaTeX` it broadly let me do the things I wanted to in terms of combining documents in a smarter way than Word allowed

Feel free to adapt bits (please credit me if it's useful), obviously the colour scheme and branding are linked to my current institution and cannot be used. 


```{r load-me, eval=TRUE, include=FALSE}
pacman::p_load_gh("sjgknight/rureporting")

xfun::pkg_load2(c("htmltools", "mime"))

```

```{r usethis-process, eval=FALSE, echo=FALSE}

#once you have a project locally, use this to setup git lcally:
usethis::use_git()

#then, this to create a github repo and link it
usethis::use_github()

#...so much easier than the other way (where I create a project and forget to create an empty repo first and have to google the command to overwrite the empty late created repo, or varations on that theme)
```


```{r eval=FALSE, include=FALSE}
install.packages("bookdown")

#bookdown::render_book('index.Rmd', 'all')


# or the development version
# devtools::install_github("rstudio/bookdown")
 
# Remember each Rmd file contains one and only one chapter, and a chapter is defined by the first-level heading `#`.

# To compile this example to PDF, you need XeLaTeX. You are recommended to install TinyTeX (which includes XeLaTeX): <https://yihui.name/tinytex/>.

#unlink("index_cache", recursive = TRUE) - is very usefl
#bookdown::serve_book()
#bookdown::render_book('index.Rmd', 'all')

```

```{r create-bib, include=FALSE, eval=params$bibupdate}

# automatically create a bib database for R packages
knitr::write_bib(.packages(), "packages.bib", tweak = TRUE) 

#extracted references from word docs using https://rintze.zelle.me/ref-extractor/ 

collection <- "http://127.0.0.1:23119/better-bibtex/export/collection?/2743773/9Q2H88RP.bibtex"
#http://127.0.0.1:23119/better-bibtex/export/collection?/2743773/all_used.bibtex
#download.file(collection,"book.bib")

#curl::curl_download(collection,"book.bib")

```


```{r set-global-knit, include=FALSE}

knitr::opts_chunk$set(echo = FALSE, out.width = "75%", warnings=F, message=F)

#this one is particularly to hide knitting messages that end up when we include the html fragments. I believe adding quiet = TRUE to render may also work 
knitr::opts_knit$set(progress=FALSE, verbose=FALSE)

```


<!-- Add anchors to # headings using `{#label}` after them, e.g., we can reference Chapter \@ref(intro). 

Reference a figure by its code chunk label with the `fig:` prefix, e.g., see Figure \@ref(fig:nice-fig). Similarly, you can reference tables generated from `knitr::kable()`, e.g., see Table \@ref(tab:nice-tab).

```{r nice-fig, fig.cap='Here is a nice figure!', out.width='80%', fig.asp=.75, fig.align='center'}
par(mar = c(4, 4, .1, .1))
plot(pressure, type = 'b', pch = 19)
```
 
You can write citations, too. For example, we are using the **bookdown** package [@R-bookdown] in this sample book, which was built on top of R Markdown and **knitr** [@xie2015].
 -->

```{r eval=FALSE, include=FALSE}
#at some point maybe explore these

library(officer)
library(magrittr)

doc_2 <- read_docx(path = "../report_draft.docx") %>% 
  body_add_par("Hello world!", style = "Normal") 

pptx_2 <- read_pptx(path = "../Attachments/evidence-base.pptx") 
doc_2 <- 
  
  body_add_docx


print(doc_2, target = "example_2.docx")

```

